---
output:
  pdf_document:
header-includes:
  - \usepackage{changepage, multicol, tabularx, tgheros}
  - \renewcommand{\familydefault}{\sfdefault}
  - \pagenumbering{gobble}
params:
  invoice_no:  0
  to:          ""
  paid:        0
  input_table: !r data.frame(Sys.Date(), 0, "", 0, stringsAsFactors = FALSE)
  date:        !r Sys.Date()
  company:     !r Sys.getenv("COMPANY")
  abn:         !r Sys.getenv("ABN")
  addr1:       !r Sys.getenv("ADDR1")
  addr2:       !r Sys.getenv("ADDR2")
  email:       !r Sys.getenv("EMAIL")
  acc_name:    !r Sys.getenv("ACC_NAME")
  bsb:         !r Sys.getenv("BSB")
  acc_no:      !r Sys.getenv("ACC_NO")
  terms:       !r Sys.getenv("TERMS")
---

\vspace{20pt}

```{r setup, echo = FALSE, message = FALSE}
library(knitr)
library(xtable)

opts_chunk$set(echo = FALSE, results = "asis")

dollar   = function(x) paste0("$", format(x, nsmall = 2))
san_col  = function(x) paste("\\bfseries", gsub("_", " ", x))
san_row  = function(x) sprintf("\\textbf{%s}", x)
```

\textbf{`r params$company` \hfill Tax Invoice}
==============================================

`r params$addr1` \hspace{10em} A.B.N. `r params$abn`

`r params$addr2`

email: `r params$email`

\vspace{20pt}

\begin{multicols}{2}

{\large\bfseries To:}

`r paste(readLines(textConnection(params$to)), collapse = "\\\\")`

\columnbreak

\begin{flushright}
\begin{tabular}{>{\bfseries}lr}
Invoice No: & `r params$invoice_no` \\
Date:       & `r params$date`
\end{tabular}
\end{flushright}

\end{multicols}

\vspace{30pt}

\begin{adjustwidth}{-\tabcolsep}{\tabcolsep}

```{r input_table}
input_table            = params$input_table
input_table$Ex_Total   = input_table[, "Hours"] * input_table[, "Ex_Rate"]

input_table_x          = input_table
input_table_x$Date     = as.character(input_table$Date)
input_table_x$Hours    = format(input_table_x$Hours, nsmall = 1)
input_table_x$Ex_Rate  = dollar(input_table_x$Ex_Rate)
input_table_x$Ex_Total = dollar(input_table_x$Ex_Total)
input_table_x          = xtable(input_table_x)
align(input_table_x)   = "lllXll"

print(input_table_x,
      hline.after                = NULL,
      sanitize.colnames.function = san_col,
      include.rownames           = FALSE,
      floating                   = FALSE,
      floating.environment       = NULL,
      table.placement            = NULL,
      comment                    = FALSE,
      tabular.environment        = "tabularx",
      width                      = "\\textwidth"
)
```

\end{adjustwidth}
\vfill

Payment may be made by Electronic Funds Transfer to:
\begin{adjustwidth}{-\tabcolsep}{\tabcolsep}
\begin{multicols}{2}
\begin{tabular}{>{\bfseries}lr}
Name: & `r params$acc_name`\\
BSB:  & `r params$bsb`\\
Acc:  & `r params$acc_no`
\end{tabular}

\hspace{\tabcolsep}\small Terms: `r params$terms`

\columnbreak

\begin{flushright}

```{r output_table}
subtotal = sum(input_table[, "Ex_Total"])
gst      = subtotal / 10L
total    = subtotal + gst
paid     = params$paid

output_table = rbind("Sub Total:"      = dollar(round(subtotal, 2)),
                     "GST:"            = dollar(round(gst, 2)),
                     "Total Inc. GST:" = dollar(round(total, 2)),
                     "Paid:"           = dollar(round(paid, 2)),
                     "Balance Due:"    = dollar(round(total - paid, 2))
output_table = xtable(output_table)
align(output_table) = "rr"

print(output_table,
      floating                   = FALSE,
      floating.environment       = NULL,
      table.placement            = NULL,
      hline.after                = NULL,
      include.colnames           = FALSE,
      add.to.row                 = list(pos     = as.list(1:5),
                                        command = rep("[10pt]", 5)),
      sanitize.rownames.function = san_row,
      comment                    = FALSE)
```
\end{flushright}

\end{multicols}
\end{adjustwidth}
